### 2015-01-17 src/introduction.Rnw
yoo

% Alex: added
Given a set of mutants and a universe of test cases, we can approximate the
minimal set of test cases required to kill those mutants.\footnote{We only
approximate this, with greedy methods, due to the high cost of computing a
perfect minimal set, as established in the test case selection literature
\cite{YooHarman}.}  Ideally, we would like a set of mutants that require
as many test cases as possible, if we assume that the original set of test
cases is populated with useful, non-redundant test cases.  While the suites
of many open source programs are far from adequate, they should satisfy that
requirement:  each test was almost always added by considerable manual labor,
and was at least believed to be useful.  Therefore, any tests omitted likely
indicate a potential to miss faults.  A good mutation selection strategy,
therefore, should 1) be as close to the original set of mutants as possible,
in terms of the test cases it requires in a minimal suite and 2) require
more test cases than a randomly selected set of mutants of the same size.

>>>>

% Alex: added
Given a set of mutants and a universe of test cases, we can approximate the
minimal set of test cases required to kill those mutants.\footnote{We only
approximate this, with greedy methods, due to the high cost of computing a
perfect minimal set, as established in the test case selection literature
\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that require
as many test cases as possible, if we assume that the original set of test
cases is populated with useful, non-redundant test cases.  While the suites
of many open source programs are far from adequate, they should satisfy that
requirement:  each test was almost always added by considerable manual labor,
and was at least believed to be useful.  Therefore, any tests omitted likely
indicate a potential to miss faults.  A good mutation selection strategy,
therefore, should 1) be as close to the original set of mutants as possible,
in terms of the test cases it requires in a minimal suite and 2) require
more test cases than a randomly selected set of mutants of the same size.
